taxize: taxonomic search and retrieval in R

### 2013-10-01 f1000_rev/taxize_appC.Rnw
Minor changes to App C.

Stable versions of taxize are available on the Comprehensive R Archive Network (CRAN) by the following process

@@

Development versions of taxize are available at Github at this linke \url{https://github.com/ropensci/taxize_}, where the codebase is actively developed. This is also a good place to report bugs, submit feature requests, etc. on the Issues page \url{https://github.com/ropensci/taxize_/issues?state=open}.

The process of installing is a little bit more involved than from CRAN, but still quite easy using the package devtools \url{http://cran.r-project.org/web/packages/devtools/index.html}. You need to install development tools if you haven't already:

@@

Once that is taken care of, install taxize from Github.

>>>>

Stable versions of taxize are available on the Comprehensive R Archive Network (CRAN) by the following process:

@@

Development versions of taxize are available at Github at this link \url{https://github.com/ropensci/taxize_}, where the codebase is actively developed. This is also a good place to report bugs, submit feature requests, etc. on the Issues page \url{https://github.com/ropensci/taxize_/issues}.

The process of installing is a little bit more involved than from CRAN, but still quite easy using the package devtools \url{http://cran.r-project.org/web/packages/devtools/index.html}.
If you don't have it yet, you can install it from CRAN:

<<installdevtools, eval=FALSE>>=
install.packages("devtools")
@

You also need to install development tools if you haven't already:

@@

Which should return `TRUE`.
Once that is taken care of, install taxize from Github.
